A Statically Checked Interface and a Checker for Tezos Smart Contracts

### 2024-01-03 reports/2023-12-31/report.tex
end-of-year-report-dec-31-2023

\section{Report January-June 2023}
\label{sec:executive-summary}

@@

Currently, the project is on track and making good progress, but Ms.\ Doan is on maternal leave
and it is unclear if she will take parental leave thereafter. If she
does, it may lead to unforseeable delays.

\subsection{January 2023 - June 2023}

\begin{itemize}
\item Proposed activity: Development of a dynamic logic as a formal foundation for symbolic interpretation of Michelson. \\
  $\Rightarrow$ This activity progressed significantly with the help of a master's
  student supervised by Thiemann. The activity started later than
  planned because the student was unavailable till the end of the
  teaching period in March.
\item Deliverable: Formalization (in Agda) of a dynamic logic for a core fragment of Michelson with soundness proof. \\
  $\Rightarrow$ This deliverable is currently in beta and will be finished when the
  master's thesis submission is due in September 2023.
\item Deliverable: Paper about this formalization (writeup starting
  July 2023). \\
  $\Rightarrow$ The paper will be based on the master's thesis, so the final writing
  starts after the submission in September. The goal is to submit to a
  conference during the winter/early spring.
\end{itemize}

\subsection{July 2023 - December 2023}
\label{sec:july-2023-december}

\begin{itemize}
\item Activity: Implementation of symbolic interpreter for a core
  fragment of Michelson in OCaml based on an SMT solver, most likely
  on Z3. \\
  $\Rightarrow$ This activity has been driven by Doan between January and June
  2023. 
\item Deliverable: Symbolic interpreter. \\
  $\Rightarrow$ The current prototype of the symbolic interpreter is available here
  \url{https://github.com/proglang/tezos-project/tree/master/static_checker}
\item Deliverable: Case studies with example contracts.
\item Deliverable: Paper or tutorial on this tool (writeup starting
  January 2024) \\
  $\Rightarrow$ A draft is available here \url{https://github.com/proglang/tezos-project/tree/master/symbolic-execution/paper}
\end{itemize}

\subsection{January 2024 - June 2024}
\label{sec:january-2024-june}

@@

\subsection{July 2024 - December 2024}
\label{sec:july-2024-december}

>>>>

\section{Progress Report July 2023 - December 2023}
\label{sec:executive-summary}

@@

Currently, the project is slightly delayed but making good progress. Ms.\ Doan
returned from  maternal leave in October 2023.

\subsection{Proposed activities for January 2023 - June 2023}

\begin{itemize}
\item Activity: Development of a dynamic logic as a formal foundation for symbolic interpretation of Michelson. \\
  $\Rightarrow$ This activity progressed significantly.  The master's
  thesis has been completed in November and is currently under review (by the examiner).
\item Deliverable: Formalization (in Agda) of a dynamic logic for a core fragment of Michelson with soundness proof. \\
  $\Rightarrow$ This deliverable is available  at
  \url{https://github.com/Barnaboss/thesis-michelsonDL}. It will be
  released after the thesis review period.
\item Deliverable: Paper about this formalization (writeup starting
  July 2023). \\
  $\Rightarrow$ The paper will be based on the master's thesis, so the final writing
  starts after completion of the thesis review. The goal is to submit to a
  conference during spring.
\end{itemize}

\subsection{Proposed activities for July 2023 - December 2023}
\label{sec:july-2023-december}

\begin{itemize}
\item Activity: Implementation of symbolic interpreter for a core
  fragment of Michelson in OCaml based on the SMT solver Z3. \\
  $\Rightarrow$ This activity has been driven by Doan between January and June
  2023 and then further after her return from maternity leave. 
\item Deliverable: Symbolic interpreter. \\
  $\Rightarrow$ The current prototype of the symbolic interpreter is available here
  \url{https://github.com/proglang/tezos-project/tree/master/static_checker}
\item Deliverable: Doan completed two case studies with example contracts.
\item Deliverable: Paper or tutorial on this tool (writeup started,
  submission planned for a deadline in spring) \\
  $\Rightarrow$ A draft is available here \url{https://github.com/proglang/tezos-project/tree/master/symbolic-execution/paper}
\end{itemize}

\subsection{Proposed activities for January 2024 - June 2024}
\label{sec:january-2024-june}

@@

\subsection{Properties activities for July 2024 - December 2024}
\label{sec:july-2024-december}
